### 2017-10-24 Draft2/Appendix.tex
[WIP] Remove P-notation
[WIP] Remove P-notation, 2
Remove prime notation

\begin{theorem}
	$P$ merges over addition and subtraction. That is,
	\begin{align*}
	P(f(n)) + P(g(n)) &= P(f(n) + g(n))\\
	P(f(n)) - P(g(n)) &= P(f(n) - g(n))
	\end{align*}
\end{theorem}

\begin{proof}
	We will consider the statement about addition first. Recall from the note at \ref{BigPProperties} that this statement is equivalent to:

	\textit{Let $f' \in P(f(n))$ and $g' \in P(g(n))$. Then $f' + g' \in P(f(n) + g(n))$.}

@@

	\begin{align*}
	\lim_{n \to \infty} \left( \frac{f' + g'}{f + g} \right) &= \lim_{n \to \infty} \left( \frac{f'}{f + g} \right) + \lim_{n \to \infty} \left( \frac{g'}{f + g} \right)\\
	&= \left( \lim_{n \to \infty} \frac{f'}{f} \right) \left( \lim_{n \to \infty} \left( \frac{f}{f + g} \right) \right) +\\
	&\ \ \ \ \left( \lim_{n \to \infty} \frac{g'}{g} \right) \left( \lim_{n \to \infty} \left( \frac{g}{f + g} \right) \right)\\
	&= \lim_{n \to \infty} \left( \frac{f}{f + g} \right) + \lim_{n \to \infty} \left( \frac{g}{f + g} \right)\\
	&= \lim_{n \to \infty} \left( \frac{f + g}{f + g} \right)\\
	&= 1
	\end{align*}

	it follows that $f' + g' \in P(f(n) + g(n))$. The statement about subtraction can be proved in a similar fashion.
\end{proof}

\begin{theorem}
	$P$ merges over multiplication and division. That is,
	\begin{align*}
	P(f(n))P(g(n)) &= P(f(n)g(n))\\
	\frac {P(f(n))} {P(g(n))} &= P\left(\frac{f(n)} {g(n)}\right)
	\end{align*}
\end{theorem}

\begin{proof}
	We will consider the statement about multiplication first. Recall from the note at \ref{BigPProperties} that this statement is equivalent to:

	\textit{Let $f' \in P(f(n))$ and $g' \in P(g(n))$. Then $f'g' \in P(f(n)g(n))$.}

	We can show this easily by multiplying the limits corresponding to $f'$ and $g'$:

	\begin{align*}
	\lim_{n \to \infty} \frac{f'(n)}{f(n)} &= 1\\
	\lim_{n \to \infty} \frac{g'(n)}{g(n)} &= 1\\
	\left( \lim_{n \to \infty} \frac{f'(n)}{f(n)} \right) \left( \lim_{n \to \infty} \frac{g'(n)}{g(n)} \right) &= 1 \cdot 1\\
	\lim_{n \to \infty} \frac{f'(n)g'(n)}{f(n)g(n)} &= 1
	\end{align*}

	it follows that $f'g' \in P(f(n)g(n))$. The statement about division can be proved by flipping the fraction for $g'$ before multiplying, resulting in

	\begin{align*}
	\lim_{n \to \infty} \frac{f'(n) / g'(n)}{f(n) / g(n)} = 1
	\end{align*}

	This implies $f' / g' \in P(f(n) / g(n))$.
\end{proof}

@@

	Now, consider any $g' \in P(g(n))$. Since

	\begin{align*}
	\lim_{n \to \infty} \frac {g'(n)} {g(n)} &= 1\\
	\left( \lim_{n \to \infty} \frac {g'(n)} {g(n)} \right) \left( \lim_{n \to \infty} \frac{g(n)}{h(n)} \right) &= 1\\
	\lim_{n \to \infty} \frac{g'(n)}{h(n)} &= 1
	\end{align*}

	it follows that $g' \in P(h(n))$, and thus $P(g(n)) \subseteq P(h(n))$. By a similar argument, it can be shown $P(h(n)) \subseteq P(g(n))$. Thus it must be true that $P(g(n)) = P(h(n))$.
\end{proof}

\subsection{Removal of Lower-Order Terms}
\label{ScrubsLowerOrderTerms}

>>>>

\begin{theorem}
	$P$ merges over addition and subtraction. That is, for functions $f$ and $g$,
	\begin{align*}
	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
	(\hat{f} + \hat{g}) \TextTilde (f + g)\\
	(\hat{f} - \hat{g}) \TextTilde (f - g)
	\end{cases}
	\end{align*}
\end{theorem}

\begin{proof}
	We will consider the statement about addition first. Recall from the note at \ref{AsymptoticProperties} that this statement is equivalent to:

	\textit{Let $\hat{f} \in P(f(n))$ and $\hat{g} \in P(g(n))$. Then $\hat{f} + \hat{g} \in P(f(n) + g(n))$.}

@@

	\begin{align*}
	\lim_{n \to \infty} \left( \frac{\hat{f} + \hat{g}}{f + g} \right) &= \lim_{n \to \infty} \left( \frac{\hat{f}}{f + g} \right) + \lim_{n \to \infty} \left( \frac{\hat{g}}{f + g} \right)\\
	&= \left( \lim_{n \to \infty} \frac{\hat{f}}{f} \right) \left( \lim_{n \to \infty} \left( \frac{f}{f + g} \right) \right) +\\
	&\ \ \ \ \left( \lim_{n \to \infty} \frac{\hat{g}}{g} \right) \left( \lim_{n \to \infty} \left( \frac{g}{f + g} \right) \right)\\
	&= \lim_{n \to \infty} \left( \frac{f}{f + g} \right) + \lim_{n \to \infty} \left( \frac{g}{f + g} \right)\\
	&= \lim_{n \to \infty} \left( \frac{f + g}{f + g} \right)\\
	&= 1
	\end{align*}

	it follows that $\hat{f} + \hat{g} \in P(f(n) + g(n))$. The statement about subtraction can be proved in a similar fashion.
\end{proof}

\begin{theorem}
	$P$ merges over multiplication and division. That is, for functions $f$ and $g$,
	\begin{align*}
	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
	\hat{f}\hat{g} \TextTilde fg\\
	\hat{f} / \hat{g} \TextTilde f / g
	\end{cases}
	\end{align*}
\end{theorem}

\begin{proof}
	We will consider the statement about multiplication first. Recall from the note at \ref{AsymptoticProperties} that this statement is equivalent to:

	\textit{Let $\hat{f} \in P(f(n))$ and $\hat{g} \in P(g(n))$. Then $\hat{f}\hat{g} \in P(f(n)g(n))$.}

	We can show this easily by multiplying the limits corresponding to $\hat{f}$ and $\hat{g}$:

	\begin{align*}
	\lim_{n \to \infty} \frac{\hat{f}(n)}{f(n)} &= 1\\
	\lim_{n \to \infty} \frac{\hat{g}(n)}{g(n)} &= 1\\
	\left( \lim_{n \to \infty} \frac{\hat{f}(n)}{f(n)} \right) \left( \lim_{n \to \infty} \frac{\hat{g}(n)}{g(n)} \right) &= 1 \cdot 1\\
	\lim_{n \to \infty} \frac{\hat{f}(n)\hat{g}(n)}{f(n)g(n)} &= 1
	\end{align*}

	it follows that $\hat{f}\hat{g} \in P(f(n)g(n))$. The statement about division can be proved by flipping the fraction for $\hat{g}$ before multiplying, resulting in

	\begin{align*}
	\lim_{n \to \infty} \frac{\hat{f}(n) / \hat{g}(n)}{f(n) / g(n)} = 1
	\end{align*}

	This implies $\hat{f} / \hat{g} \in P(f(n) / g(n))$.
\end{proof}

@@

	Now, consider any $\hat{g} \in P(g(n))$. Since

	\begin{align*}
	\lim_{n \to \infty} \frac {\hat{g}(n)} {g(n)} &= 1\\
	\left( \lim_{n \to \infty} \frac {\hat{g}(n)} {g(n)} \right) \left( \lim_{n \to \infty} \frac{g(n)}{h(n)} \right) &= 1\\
	\lim_{n \to \infty} \frac{\hat{g}(n)}{h(n)} &= 1
	\end{align*}

	it follows that $\hat{g} \in P(h(n))$, and thus $P(g(n)) \subseteq P(h(n))$. By a similar argument, it can be shown $P(h(n)) \subseteq P(g(n))$. Thus it must be true that $P(g(n)) = P(h(n))$.
\end{proof}

\subsection{Removal of Lower-Order Terms}
\label{RemovesLowerOrderTerms}
